Estimating Trending Topics on Twitter with Small Subsets of the Total Data

### 2015-01-12 521_project_paper.tex
Changes to paper

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsmath}
\usepackage{amsthm}

@@

To this structure we add another layer that combines these Count-Min sketches into a single Count-Min sketch that depreciates the value of older data.  This aggregate Count-Min sketch stores the values $\bar{M} + \sum\limits_{j=0}^{\log⁡(T)} \frac{M^j}{2^j}$ where $\bar{M}$ is the Count-Min sketch storing today's data, $M^j$ is the Count-Min sketch storing the data for the sketch with a $2^j$ resolution, and $T$ is an upper bound on the number of days stored by the data structure.  In section \ref{Correct} we will show that this aggregate Count-Min sketch weights the hashtags that occurred $i$ days ago with value approximately $\frac{1}{2i}$.

@@

\begin{algorithm}
\caption{Time Aggregation for the Hokusai structure}\label{alg1}
\begin{algorithmic}[1]
\ForAll {$i$}
	\State Initialize Count-Min sketch $M^i = 0$
\EndFor
\State Initialize $t = 0$, $\bar{M} = 0$, and $A = 0$
\While {data arrives}
	\State Aggregate data into sketch $\bar{M}$ for current day while also adding this data to $A$
	\State $t \leftarrow t + 1$ (increment counter)
	\State $A \leftarrow A - \bar{M}$
	\For {$j = 0$ to argmax \{$l$ where $t$ mod $2^l = 0$\}}
		\State $A \leftarrow A + 2^{-j}(\bar{M} - M^j)$
		\State $T \leftarrow \bar{M}$ (back up temporary storage)
		\State $\bar{M} \leftarrow \bar{M} + M^j$ (increment cumulative sum)
		\State $M^j \leftarrow T$ (new value for $M^j$)
	\EndFor
	\State $\bar{M} \leftarrow 0$ (reset aggregator)
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

Maybe put table here of all tunable parameters mentioned in the paper to remind readers what they refer to.

\subsubsection{Time analysis}

Let s = size of heap = number of distinct hashtags seen in last y minutes.

>>>>

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}

@@

To this structure we add another layer that combines these Count-Min sketches into a single Count-Min sketch that depreciates the value of older data.  This aggregate Count-Min sketch stores the values $\bar{M} + \sum\limits_{j=0}^{\log⁡(T)} \frac{M^j}{2^j}$ where $\bar{M}$ is the Count-Min sketch storing today's data, $M^j$ is the Count-Min sketch storing the data for the sketch with a $2^j$ resolution, and $T$ is an upper bound on the number of days stored by the data structure.  In section \ref{Correct} we will show that this aggregate Count-Min sketch weights the hashtags that occurred $i > 0$ days ago with value approximately $\frac{1}{i}$.

@@

\begin{algorithm}
\caption{Time Aggregation for the Hokusai structure}\label{alg1}
\begin{algorithmic}[1]
\ForAll {$i$}
	\State Initialize Count-Min sketch $M^i = 0$
\EndFor
\State Initialize $t = 0$
\State Initialize Count-Min sketches $\bar{M} = 0$ and $A = 0$
\While {data arrives}
	\State Aggregate data into sketch $\bar{M}$ for current day while also adding this data to $A$
	\State $t \leftarrow t + 1$ (increment counter)
	\State $A \leftarrow A - \bar{M}$
	\For {$j = 0$ to argmax \{$l$ where $t$ mod $2^l = 0$\}}
		\State $A \leftarrow A + 2^{-j}(\bar{M} - M^j)$
		\State $T \leftarrow \bar{M}$ (back up temporary storage)
		\State $\bar{M} \leftarrow \bar{M} + M^j$ (increment cumulative sum)
		\State $M^j \leftarrow T$ (new value for $M^j$)
	\EndFor
	\State $\bar{M} \leftarrow 0$ (reset aggregator)
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]
\caption{Variables referenced in this section}
\begin{tabular}{@{}ll@{}}
\toprule
Symbol & Meaning                                                           \\ \midrule
m      & Number of tables for each Count-Min sketch                        \\
n      & Size of each hash table in each Count-Min sketch                  \\
s      & Number of distinct hashtags in the Current Window                 \\
T      & Upper bound on the number of days worth of data stored in History \\
y      & Minutes of data contained in the Current Window                   \\ \bottomrule
\end{tabular}
\end{table}
\subsubsection{Time analysis}
